From physical principles to ???

### 2016-02-18 2015CompleteDerivation/completeDerivation.tex
More notes on classical systems

@@

@@

@@

% TODO: need to understand a valid notation for composite state as infinite sum. The densities is the coefficient, the basis are are states, what is the differential?

Find smallest object that can have an invariant density. $\mathcal{c}= \int\limits_{T^*\mathbbm{Q}} \rho(q,k) \mathcal{e}(q,k)dq\wedge dk$

@@

>>>>

TODO: Still not clear what's the best way to introduce things. We do want to show that state variable are maps from states to "labels". We want to call discrete variables those that map to integer and continuous variables those that map to real numbers. Then we want to concentrate on state space that can be described by a finite number of either discrete variables or continuous variables. State vector may not be valid in general: e.g. we can't assume we have a single chart for the whole space.

@@

TODO: should we note already that the state space is a Lie group?

@@

Need to define inner product. Introduce $Q:\mathcal{C} \to \mathbbm{R}$ amount of "stuff" of the system. $Q:\mathcal{S}\times\mathcal{C} \to \mathbbm{R}$ amount of stuff of the composite system in that particular state. We can use those those to construct inner product, and to show that states are bounded, but: norm induced by the inner product is not physical.

\begin{defn}\label{classical_inner_product}
	TODO: there exist an inner product.
\end{defn}

@@

TODO: need to understand a valid notation for composite state as infinite sum. The densities is the coefficient, the basis are are states, what is the differential?

Find smallest object that can have an invariant density (inner product). $\mathcal{c}= \int\limits_{T^*\mathbbm{Q}} \rho(q,k) \mathcal{e}(q,k)dq\wedge dk$

@@

TODO: generalization of inner product gives us $\int \rho_1(q, p) \rho_2(q, p) dq\wedge wp$. Space of continuous functions is not a complete metric space. Extend to square integrable. Get a Hilbert space. But topology is not a second countable: more than aleph 1. No physical justification, in fact we introduce unphysical functions (i.e. 0 rational, 1 irrational). Discontinuous functions not physical states: they are not distinguishable.
